Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks

### 2014-11-19 paper-postreview/conclusions.tex
working on adding the second goal everywhere

This work demonstrates that asking the proper question, and then crafting an appropriate weighting scheme to answer that question, is an unavoidable first step for community detection in online social media.\alert{need to add to the paragraph the asking multiple question} More generally, this work illustrates that without a clear definition of community, many rich and interesting communities present in online social networks remain invisible. Question-oriented community detection can bring those hidden communities into the light.

>>>>

This work demonstrates the utility of a multi-faceted question-oriented approach to community detection. This work shows that crafting \emph{several} facet-driven weighting schema, doing community detection for each weighting scheme and then comparing the similarities and differences across community types, is an unavoidable process for unconvering the multi-leveled community structure present in online social media. More generally, this work illustrates that without a clear definition of community---or even only using a \emph{single} definition of community---many rich and interesting communities present in online social networks remain invisible. Multi-faceted question-oriented community detection can bring those hidden communities into the light.

### 2014-11-19 paper-postreview/intro.tex
working on adding the second goal everywhere

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Girvan-Newman algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed. As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multi-faceted question-focused} approach. We believe that in order to understand all of the communities present in a network, it is important to take two crucial steps: 
\begin{enumerate}
\item Form a clear question about what \emph{type} of community we wish to consider---{\it e.g.,} are we looking for groups of friends? or for groups of people having a common interest?---and then perform community detection with that question in mind.
\item Ask more than one question about the users in a network. Do several rounds of community detection, each of which is aimed at revealing a new facet of the communities present in the network. 
\end{enumerate}

@@

Studying the intersections and lack-thereof of the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks allow us to build a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone. In this paper, we explore the relation between these various possible networks and their corresponding communities. We begin by describing the methodologies used to generate the various types of networks, and infer their community structure. We then explore how the communities of users differ depending on the type of network used. Finally, we explore how communication patterns differ across and within the different community types. We conclude by illustrating that this multi-faceted question-oriented approach to community detection provides interesting insight into the intricate multi-faceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed. 
%\section{Related Work}

>>>>

%A large body of work exists on methods for automatic detection of communities within networks~\cite{newman2004fast,newman2004finding,rosvall2008maps,blondel2008fast,LancichinettiPlos}. See~\cite{fortunato2010community} for a recent review. 
A large body of work exists on methods for automatic detection of communities within networks, {\it e.g.,} the stochastic blockmodel~\cite{Holland1983} (and its recent generalization to weighted networks~\cite{Aicher26062014}), the Girvan-Newman algorithm~\cite{newman2004finding}, clique percolation~\cite{PalEtAl05}, Infomap~\cite{Rosvall08mapsof}, Louvain~\cite{blondel2008fast}, and the recently introduced OSLOM~\cite{LancichinettiPlos}.
All these methods begin with a given network, and then attempt to uncover structure present in the network, \emph{i.e.,} they are agnostic to how the network was constructed. As opposed to this agnostic analysis, we propose---and illustrate the importance of---a \emph{multi-faceted question-focused} approach. We believe that in order to understand all of the communities present in a network, it is important to take two crucial steps: 
\begin{enumerate}
\item Form a clear question about what \emph{type} of community under consideration---{\it e.g.,} are we looking for groups of friends? or for groups of people having a common interest?---and then perform community detection with that question in mind.
\item Ask more than one question about the users in a network and perform several rounds of community detection, each of which is aimed at revealing a new facet of the communities present in the network. 
\end{enumerate}

@@

Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone. In this paper, we explore the relation between these various possible networks and their corresponding communities. We begin by describing the methodologies used to generate the various types of networks, and infer their community structure. We then explore how the communities of users differ depending on the type of network used. Finally, we explore how communication patterns differ across and within the different community types. We conclude by illustrating that this multi-faceted question-oriented approach to community detection provides interesting insight into the intricate multi-faceted structure of several different users' communities; information that would not be available if only a single form of community detection was performed. 
%\section{Related Work}

### 2014-11-19 paper-postreview/results.tex
working on adding the second goal everywhere

As an aside, it is interesting to examine which users had the greatest PV-AC in these communities. Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. %Said differently, higher transfer entropy, or a higher reduction in uncertainty, implies more influence. 
Interestingly, among the highest PV-AC users in these communities--- those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these communities discuss Colorado and these accounts provide information on this topic. However, this does provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity with a communities activity on social media networks.

Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", % ranked using the total outgoing strength in the activity-based network, 
 happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as highly influential.
% members, as categorized by transfer entropy. 
This suggests that activity-based or information-theoretic influence may be useful in finding influential members purely based on their temporal tweet history while completely ignoring both tweet content and social status.

>>>>

As an aside, it is interesting to examine which users had the highest PV-AC in these communities. Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter.
Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these communities discuss Colorado and these accounts provide information on this topic. This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity with a communities activity on a social media network. However, more work needs to be done to quantify this more fully.

Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers",
 happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories. While we do not believe this information theoretic measure can capture social influence in its entirety, 
% members, as categorized by transfer entropy. 
this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status. However, a deeper analysis would need to be carried out to verify this finding.
